\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

To set up a variational recursion of the form \eqref{InfiniteDimProxOpDef} for \eqref{TransformedPDEivp}, we set $(\Phi,{\rm{dist}}) \equiv \left(\widetilde{\Phi},\widetilde{W}\right)$ where
\begin{align}
\widetilde{\Phi}(\tilde{\rho}) := \int_{\mathbb{T}^{n} \times \mathbb{R}^{n}}\left(F(\boldsymbol{\eta})+\frac{1}{2} \log \tilde{\rho}\right) \tilde{\rho}\: \mathrm{d} \boldsymbol{\xi} \mathrm{d} \boldsymbol{\eta},
\label{Phitilde}	
\end{align}
and 
\begin{align}
\widetilde{W}^{2}\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right):=&\inf _{\pi \in \Pi\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right)}\!\int_{\mathbb{T}^{2 n} \times \mathbb{R}^{2 n}}\!\!\left\{\left\|\overline{\boldsymbol{\eta}}-\boldsymbol{\eta}+h \nabla_{\boldsymbol{\xi}} U(\boldsymbol{\xi})\right\|_{2}^{2}\right.\nonumber\\
&\hspace*{-0.2in}\left.+12\left\|\frac{\overline{\boldsymbol{\xi}}-\boldsymbol{\xi}}{h}-\frac{\overline{\boldsymbol{\eta}}+\boldsymbol{\eta}}{2}\right\|_{2}^{2}\right\} \mathrm{d} \pi(\boldsymbol{\xi}, \boldsymbol{\eta}, \overline{\boldsymbol{\xi}}, \overline{\boldsymbol{\eta}}).
\label{Wtilde}	
\end{align}
In \eqref{Wtilde}, $\Pi\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right)$ denotes the collection of all joint PDFs supported on $\mathbb{T}^{2 n} \times \mathbb{R}^{2 n}$ that have finite second raw moments, with the first marginal $\tilde{\varrho}$, and the second marginal $\tilde{\varrho}_{k-1}$.

@@

To compute \eqref{KineticProx}, we employ the probability-weighted scattered point cloud-based proximal algorithm proposed in \cite{caluya2019TAC}.

>>>>

To set up a variational recursion of the form \eqref{InfiniteDimProxOpDef} for \eqref{TransformedPDEivp}, we set $(\Phi,{\rm{dist}}) \equiv \left(\widetilde{\Phi},\widetilde{W}\right)$ where
\begin{align}
\widetilde{\Phi}(\tilde{\rho}) := \int_{\mathbb{T}^{n} \times \mathbb{R}^{n}}\left(F(\boldsymbol{\eta})+\frac{1}{2} \log \tilde{\rho}\right) \tilde{\rho}\: \mathrm{d} \boldsymbol{\xi} \mathrm{d} \boldsymbol{\eta},
\label{Phitilde}	
\end{align}
and 
\begin{align}
\widetilde{W}^{2}\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right):=\!&\inf _{\pi \in \Pi\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right)}\!\int_{\mathbb{T}^{2 n} \times \mathbb{R}^{2 n}}\!\!\left\{\left\|\overline{\boldsymbol{\eta}}-\boldsymbol{\eta}+h \nabla_{\boldsymbol{\xi}} U(\boldsymbol{\xi})\right\|_{2}^{2}\right.\nonumber\\
&\hspace*{-0.2in}\left.+12\left\|\frac{\overline{\boldsymbol{\xi}}-\boldsymbol{\xi}}{h}-\frac{\overline{\boldsymbol{\eta}}+\boldsymbol{\eta}}{2}\right\|_{2}^{2}\right\} \mathrm{d} \pi(\boldsymbol{\xi}, \boldsymbol{\eta}, \overline{\boldsymbol{\xi}}, \overline{\boldsymbol{\eta}}).
\label{Wtilde}	
\end{align}
In \eqref{Wtilde}, $\Pi\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right)$ denotes the collection of all joint PDFs supported on $\mathbb{T}^{2 n} \times \mathbb{R}^{2 n}$ that have finite second raw moments, with the first marginal $\tilde{\varrho}$, and the second marginal $\tilde{\varrho}_{k-1}$.

@@

To numerically compute \eqref{KineticProx}, we employ the probability-weighted scattered point cloud-based proximal algorithm proposed in \cite{caluya2019TAC}.
